---
name: Shira
surname: Salingre
position: "Data Analyst"
address: "Barcelona, Catalonia, Spain"
www: shirasal.github.io
email: "shira.salin@gmail.com"
phone: "+34-603-522-149"
# twitter: shira_salin
github: shirasal
linkedin: shira-salingre
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "74c5c3"
output: 
  vitae::awesomecv:
    page_total: true
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(vitae)
library(here)
library(kableExtra)

```

```{r functions}
readExcelSheets <- function(filename){
  # read all sheets in .xlsx 
  all <- readxl::excel_sheets(filename)
  # import each sheet into a list using readxl::read_excel
  list <- lapply(all, function(x) readxl::read_excel(filename, sheet = x))
  # save sheet name for each sheet (list)
  names(list) <- all
  # breaks up list and creates a dataframe for each sheet with df names matching sheet names
  list2env(list, envir = .GlobalEnv)
}

```

```{r load-data, message=F, results='hide'}

filename <- here::here("shira_salingre_cv_data.xlsx")
readExcelSheets(filename)

```

# Short introduction

-   Data analyst with quantitative research background.
-   Organised, curious and passionate person.
-   **Love turning DATA into KNOWLEDGE**.

<!-- # Professional Summary -->

<!-- This is a good opportunity to introduce yourself professionally and summarise -->

<!-- why your skills are well suited to the job you are applying for!") -->

# Experience

```{r}
industry %>% 
  detailed_entries(what = institution,
                   when = paste(start_date, end_date, sep = "-"),
                   with = role,
                   where = where,
                   why = details)
```

# Education

```{r}
education %>% 
  detailed_entries(what = institution,
                   when = year,
                   with = degree,
                   where = where,
                   why = details)

```

# Skills

```{r, fig.width = 7, fig.asp = .3}
skills %>%
  select(Type, Skill, Score) %>% 
  mutate(rank_order = Score) %>% 
  expand(nesting(Type, Skill, rank_order), Score = 1:5) %>%
  left_join(mutate(skills %>% select(Type, Skill, Score), achieved = TRUE)) %>%
  group_by(Type, Skill) %>%
  mutate(achieved = lag(cumsum(coalesce(achieved, FALSE)) < 1, default = TRUE)) %>% 
  ggplot() +
  aes(x = Score, y = reorder(Skill, rank_order), color = achieved) + 
  geom_point(size = 4) +
  facet_wrap(~Type, scales = "free", strip.position = "right") +
  labs(x = "", y = "") +
  scale_x_continuous(expand = expansion(add = 0.5)) +
  scale_color_manual(values = c("transparent", "#74c5c3"), guide = "none") +
  theme_minimal() + 
  theme(
    axis.text.x = element_blank(),
    axis.ticks = element_blank(),
    strip.background = element_rect(fill = "lightgray", color = NA),
    strip.text = element_text(face = "bold"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

```

## Soft skills

-   Pro-active
-   Organised, self-managed and reliable
-   Nice, friendly and open-minded
-   Great communicator
-   Results oriented and passionate about data
-   Curious and ever-learning
